resistanceModelNotesAndy

### 2015-06-09 resistanceModelNotesAndy.Rmd
progress notes

>>>>

** 9/6/15 ** 4-5

Chatting with Ian & working out that both sequential and mixture2 scenarios can also be done by post-processing of the output file.

Now looking at setting up sensiAnPaper1() to run the sensitivity analysis for the paper.
Realising that I might not be able to call sensiAn1 and setInputSensiScenarios() because of some of the dependencies between parameters.

Particularly that `P_2` needs to be set as a proprtion of `P_1`.

Actually sensiAnPaper1() can be much more straightforward if it has hardcoded args and doesn't need to be so flexible.
